% Paper, encoding and fonts settings
\documentclass[a4paper, openright, twoside, 12pt]{report}
\usepackage{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{dsfont}
\usepackage{fancyhdr}
\usepackage{emptypage}
\usepackage[table]{xcolor}

% Document structure and layout
\usepackage{pdfpages}
\usepackage[toc,page]{appendix}
\usepackage{standalone}
\usepackage[absolute]{textpos}
\usepackage{setspace}
\usepackage{adjustbox}
\usepackage{rotating}

% Graphics and plotting
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{graphicx}
\graphicspath{ {graphics/} }

% Math, physics and numbers
\usepackage{amsmath}
\usepackage{siunitx}

% Extra features and enhancements
\usepackage{cite}
\usepackage[toc, acronym]{glossaries}
% Tables
\usepackage{multirow}
\usepackage{nicematrix}
\usepackage{booktabs}
% Captions
\usepackage[justification=centering]{caption}
\usepackage{subcaption}
% Listings
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{minted}
% Make sure that hyperref is last loaded package
\usepackage[hidelinks]{hyperref}

% Pgfplots configuration
\pgfplotsset{compat=newest}
\usepgfplotslibrary{statistics}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[LO]{\nouppercase{\it\rightmark}}
\fancyhead[RE]{\nouppercase{\it\leftmark}}
\fancyhead[LE,RO]{\it\thepage}

\glsenablehyper
\makeglossaries

\begin{document}
\pagenumbering{gobble}

\input{titlepage}

% Create minted environment for long listings with page breaks
\newenvironment{longlisting}{\captionsetup{type=listing}}{}

\cleardoublepage

% Introductory pages
\begin{abstract}
This work aims to enhance super-resolution satellite imaging by using
data augmentation techniques based on deep learning algorithms.
Super-resolution is a technology that enables upscaling images to a higher
resolution with more refined details and improved quality.
Such image-enhancing techniques are nowadays undergoing rapid development
thanks to advancements in deep learning and convolutional neural networks.
Deep learning is an approach in which training data plays a key role in the
outcome and quality of the solution.
The size and quality of the dataset used to train super-resolution networks are
crucial to achieving the best results.
This is especially significant when working with satellite images, which are
effortful to acquire in large numbers.
Thus, when training a super-resolution network, it may be worth incorporating
data augmentation techniques.
Data augmentation is a process that intends to enlarge and improve training
datasets for machine learning by transforming, multiplying, or generating data.
In the field of super-resolution, the data creation process has been traditionally done using resampling techniques; however, this work aims to use deep learning to generate the datasets for training super-resolution algorithms.
The following chapters provide an overview of modern super-resolution solutions
and a proposal of a set of deep learning algorithms to generate the training datasets.
The results of the work are evaluated by testing super-resolution networks that
were trained on the datasets created during the project.

{
  \vspace{1em}
  \noindent
  \textbf{\textit{Keywords:}} super-resolution, deep learning, data augmentation
}
\end{abstract}

\tableofcontents
\cleardoublepage

\pagenumbering{arabic}

% Chapters
\chapter{Introduction}
\label{ch:introduction}
\input{chapters/introduction}

\chapter{Analysis of the related work}
\label{ch:analysis}
\input{chapters/analysis}

\chapter{Scope of work}
\label{ch:scope}
\input{chapters/scope}

\chapter{Data augmentation with the usage of deep learning}
\label{ch:augmentation}
\input{chapters/augmentation}

\chapter{Super-resolution training and evaluation}
\label{ch:sr-evaluation}
\input{chapters/evaluation}

\chapter{Summary}
\label{ch:summary}
\input{chapters/summary}

\begin{appendices}
    \input{chapters/appendices}
\end{appendices}

\input{glossary}
\printglossary[type=\acronymtype]

% Lists of objects
\listoffigures
\listoftables
\listofalgorithms
\listoflistings

% Bibliography
\bibliographystyle{plain}
\bibliography{references}

\end{document}
